\myTitle

### 2023-11-28 body-text-of-paper.tex
matt's updates to results

SNP filtering resulted in 14,233 loci that were used for subsequent analysis.
Using the 160 empirical samples, ADMIXTURE results supported the identification of
3 genetic clusters (SUPPLEMENTAL FIGURE). Admixture $q$ values clearly grouped individuals
from each of the core populations into 3 clusters while the 40 individuals from the contact regions were
highly admixed (SUPPLEMENTAL FIGURE). The
$F_{ST}$ divergence from ADMIXTURE was:
$F_{ST} = 0.24$ for Pop1-Pop2,
$F_{ST} = 0.14$ for Pop1-Pop14 and
$F_{ST} = 0.13$ for Pop2-Pop14. The simulated hybrid classes produce
the expected range of admixture with $F_1$ and $F_2$ individuals having mean $q=0.5$, with $F_2$ individuals having
more variation. Backcrossed individuals have higher ancestry associated with the backcrossed population with $q$
approximately $0.75$ ($BC_1$) and $0.875$ ($BC_2$) (Figure~\ref{fig:pig-sim-qs}). MATT NEEDS TO AUGMENT AND 
REVISE THE RESULTS

%%%
\begin{figure*}
\newcommand{\pigsimsqscap}{\footnotesize MATT NEEDS TO ADD CAPTION.}
\includegraphics[width=0.96\textwidth]{figures/simulation-density-multipanel.pdf}
\caption[\pigsimsqscap]{\pigsimsqscap}
\label{fig:pig-sim-qs}
\end{figure*}
%%%

>>>>

SNP filtering resulted in 14,233 loci that were used for subsequent analysis.
Using the 160 empirical samples, ADMIXTURE results supported the identification of
$K=3$ genetic clusters grouped individuals from each of the core populations into 3 clusters 
while the 40 individuals from the contact regions were highly admixed. The
$F_\mathrm{ST}$ divergence from ADMIXTURE was:
$F_\mathrm{ST} = 0.24$ for Pop1-Pop2,
$F_\mathrm{ST} = 0.14$ for Pop1-Pop3 and
$F_\mathrm{ST} = 0.13$ for Pop2-Pop3.

The simulated hybrid classes produce
the expected range of admixture with $F_1$ and $F_2$ individuals having mean $Q=0.5$, with $F_2$ individuals having
more variation (Figure~\ref{fig:pig-sim-qs}A). 
Backcrossed individuals have higher ancestry associated with the backcrossed population with mean $Q$
approximately $0.75$ ($BC_1$) and $0.87$ ($BC_2$) (Figure~\ref{fig:pig-sim-qs}A). Notably, the simulated 
$F_1$ hybrids have the most variation in the distribution of the $Q$ values associated with each of the genetic clusters. 
When the estimated Q values for the $F_1$ hybrids are separated by the population combinations, 
$F_1$ hybrids for Pop1-Pop2 have the least variation around $q=0.5$ (standard deviation 
= 0.008), while Pop1-Pop3 and Pop2-Pop3 
have higher variation (standard deviation = 0.011-0.016) (Figure~\ref{fig:pig-sim-qs}B). Also, all $Q$ 
distributions for $F_1$ hybrids, regardless of population combination, center around 
$0.50$ except for the two distributions 
of Pop3, which have a mean of $Q=0.49$ (Figure~\ref{fig:pig-sim-qs}B).
The differences among these 
distributions of $Q$ values for the simulated data reflect the genetic differences observed 
in the empirical data, specifically, that genetic differentiation is highest between Pop1 and Pop2 and that 
Pop14 is the most admixed population with ancestry contributions from both Pop1 and Pop2.

%%%
\begin{figure*}
\newcommand{\pigsimsqscap}{\footnotesize (A) The density of the estimated Q values from ADMIXTURE for 
the simulated runs are 
grouped across all population-combinations for each hybrid class and colored by the $K$ genetic cluster 
(e.g., the Pop1 density plot for the $F_{1}BC_1$ plots the Pop1 genetic cluster for both 
the Pop1-Pop2 and Pop1-Pop3 combinations). The density plots across the $K$ 
genetic clusters are mostly similar with the most variation among the genetic clusters evident in 
the $F_1$ plot. (B) Plotting the density of the estimated Q values from ADMIXTURE for the $F_1$ hybrids, 
separated by the population combinations, reveals the least variance in estimated Q values for 
Pop1-Pop2 compared to Pop1-Pop3 and Pop2-Pop3. Note that these population combinations group the 
reciprocal population combination in each plot (e.g., "Pop1_Pop2" has simulations 
from both Pop1-Pop2 and Pop2-Pop1).}
\includegraphics[width=0.96\textwidth]{figures/simulation-density-multipanel.pdf}
\caption[\pigsimsqscap]{\pigsimsqscap}
\label{fig:pig-sim-qs}
\end{figure*}
%%%
